Implicit yaddayadda

### 2011-10-25 papers/PLDI2012/implicitization.tex
experiments

In this section, our experimental results come from the analysis of various
open-source projects listed in Figure \ref{fig:projects}, written in C, C++ and
Fortran.
\begin{figure}[!h]
	\centering
\begin{tabular}{|l|l|l|} \hline
	Name & LOC & $|P_R|$ \\ \hline
	a2ps & 55k & 2012\\
	gawk & 59k & 902\\ 
	gnuchess & 38k & 1222\\ 
	gnugo & 83k & 2801\\
	grep & 35k & 820\\
	gzip & 27k & 494\\
	lapack/blas & 954k & 16422\\
	make & 34k & 993\\ 
	sed & 23k & 292\\
	tar & 73k & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{figure}

@@

Figures \ref{fig:techniques} shows the results of various comparisons between
the different analysis techniques.

\begin{table*}
\begin{center}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|c||c|c|c||} \hline
\textbf{Benchmark} & \multicolumn{3}{c||}{\textbf{G/S}}
& \multicolumn{3}{c||}{\textbf{PF/S}}
& \multicolumn{3}{c||}{\textbf{PF/G}}
& \multicolumn{3}{c||}{\textbf{G+PF/PF}}
& \multicolumn{3}{c||}{\textbf{G+PF/G}} \\ \cline{2-16}
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} \\
 \hline
 \input{table1.tex}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focused} technique (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm. \textbf{lt} column gives the
percentage of invariants more precise with the left-side technique,
\textbf{gt} the percentage of invariants better with the right-side technique,
and \textbf{un} gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
\end{table*}

>>>>

In this section, our experimental results come from the analysis of various
open-source projects listed in Figure \ref{fig:projects}, written in C, C++ and
Fortran.
\begin{figure}[!h]
	\centering
\begin{tabular}{|l|r|r|} \hline
	Name & LOC & $|P_R|$ \\ \hline
	a2ps & 55k & 2012\\
	gawk & 59k & 902\\ 
	gnuchess & 38k & 1222\\ 
	gnugo & 83k & 2801\\
	grep & 35k & 820\\
	gzip & 27k & 494\\
	lapack/blas & 954k & 16422\\
	make & 34k & 993\\ 
	sed & 23k & 292\\
	tar & 73k & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{|l||r|r|r||r|r|r||r|r|r||r|r|r||r|r|r||} \hline
\textbf{Benchmark} & \multicolumn{3}{c||}{\textbf{G/S}}
& \multicolumn{3}{c||}{\textbf{PF/S}}
& \multicolumn{3}{c||}{\textbf{PF/G}}
& \multicolumn{3}{c||}{\textbf{G+PF/PF}}
& \multicolumn{3}{c||}{\textbf{G+PF/G}} \\ \cline{2-16}
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} \\
 \hline
 \input{table1.tex}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focused} technique (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm. \textbf{lt} column gives the
percentage of invariants more precise with the left-side technique,
\textbf{gt} the percentage of invariants better with the right-side technique,
and \textbf{un} gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
\label{tab:techniques}
\end{table*}

Table \ref{tab:techniques} gives the results of the comparison between the
different analysis techniques, applied to the benchmarks described in Figure
\ref{fig:projects}. These results are also summarized by Figure \ref{fig:techniques}.

\emph{Guided Static Analysis} from \citet{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.37\%$ of the control points
in $P_R$.
\emph{Path-focused} technique from \citet{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $7.28\%$ of the cases. However, it also looses precision in an
important number ($2.93\%$) of control points.
Our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective.

While experiencing with techniques that use SMT-solving, we encountered some
limitations due to non-linear arithmetic in the analyzed programs. Indeed, 
the SMT-solver is not able to decide the satisfiability of some SMT-formulae
expressing the semantics of non-linear programs. 
In this case, we skipped the function for which the SMT-solver returned the
``unknown'' result.
This limitation occured very rarely in our experiments, except for the analysis
of \emph{Lapack/Blas}, where 798 over the 1602 functions have been skipped.
In such cases, such a technique should make the SMT-formula simpler to solve by using
for instance \emph{linearization}. However, such transformations are not
implemented in our analyzer.
